The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-08-22 floats/figures.tex
Arjen's corrections in float captions

% fig:locmap
\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=8cm]{cordillera-climate-locmap}
	\end{center}
	\caption{Shaded relief map of northern North America. The frame delimits this study's modelling domain. The outlines of the former ice sheets depict ice cover at 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) after \cite{dyke-2004}. The background map was made with ETOPO1 (\cite{data:etopo1}) and Natural Earth Data (\cite{data:naturalearth}).}
	\label{fig:locmap}
\end{figure}

% fig:temp
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-temp}
	\end{center}
	\caption{Summer temperature maps from the five datasets used in this study and winter temperature map from the WorldClim dataset.}
	\label{fig:temp}
\end{figure*}

% fig:prec
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-prec}
	\end{center}
	\caption{Winter precipitation rate maps from the five datasets used in this study and summer precipitation map from the WorldClim dataset.}
	\label{fig:prec}
\end{figure*}

>>>>

% fig:locmap
\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=8cm]{cordillera-climate-locmap}
	\end{center}
	\caption{Shaded relief map of northern North America with the extent of the Cordilleran (CIS), Laurentide (LIS) and Innuitian (IIS) ice sheets at 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) \citep{dyke-2004}. The background map consists of ETOPO1 (\cite{data:etopo1}) and Natural Earth Data (\cite{data:naturalearth}).}
	\label{fig:locmap}
\end{figure}

% fig:temp
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-temp}
	\end{center}
	\caption{Summer (JJA) and winter (DJF) temperature maps from CFSR (Climate System Forecast Reanalysis), ERA-Interim reanalysis, NARR (North American Regional Reanalysis), and NCEP/NCAR reanalysis climatologies.}
	\label{fig:temp}
\end{figure*}

% fig:prec
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-prec}
	\end{center}
	\caption{Summer (JJA) and winter (DJF) precipitation maps from CFSR (Climate System Forecast Reanalysis), ERA-Interim reanalysis, NARR (North American Regional Reanalysis), and NCEP/NCAR reanalysis climatologies.}
	\label{fig:prec}
\end{figure*}
